---
output: github_document
---


```{r, include = FALSE}

knitr::opts_chunk$set(
  collapse = TRUE, 
  comment = "#>",
  fig.path = "man/figures/README-", 
  out.width = "100%"
  )

```

# openlibraryR <img src = "man/figures/openlibraryR_sm.png" width = "180px" align = "right" />

openlibraryR is an R package that provides a simple wrapper for the [Open Library API](https://openlibrary.org/dev/docs/api/books).

[Open Library](https://openlibrary.org) is a digital repository of publication data that aims to make "all of the published works of humankind available to everyone in the world" that is part of archive.org. 

Hex sticker icon by [mangsaabguru](https://www.flaticon.com/authors/mangsaabguru).

## Installation  

You can install the development version of openlibraryR from Github:  

```{r, eval = FALSE}
devtools::install_github("walkerkq/openlibraryR")
```

## Getting Started  

You do not need an account or key to access the Open Library API. There is only method provided which returns book details from an ISBN (International Standard Book Number).   

```{r}
my_book <- openlibraryR::get_books(book_id = '0486282112')

str(my_book)
```



